A quantitative framework for investigating the reliability of empirical network construction

### 2018-11-08 manuscript/reply_to_reviewers.tex

% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Associate Editor}
% ---------------------------------------

	\begin{refquote}
	Your manuscript has been assessed by four different referees who agree that you touch upon a very important problem. However, they all feel your manuscript needs substantial improvements. They provide excellent advise on how to revise your manuscript and you should carefully consider all their comments. Overall, you do not acknowledge important past contributions and do not clearly explain the importance of the methodological issues you cover in your study. Importantly, referee 1 feels the real novelty of your study is the consideration of the importance and complexity of choosing prior information in constructing networks. Obviously, this is an issue in the context of Bayesian approaches, which are not necessarily well understood by empiricists, precisely the audience your manuscript should address. Please, follow very closely the suggestions of the referees when revising your manuscript.

	\end{refquote}

	\textbf{R:} We appreciate the thoughtful feedback by the four referees. We take particular note of the comments regarding the structure and grounding of our introduction and have worked to address this. Reviewer 2's comments take a different view of the purpose and scope of the manuscript than the other reviewers; we respect their ideas but feel that some are beyond the scope of the present manuscript. In particular, we do not feel that a full simulation study is necessary given the simplicity of our framework. We emphasize that we are not introducing a software package (although we do provide simple code to aid those who are new to the field), nor are we introducing an entirely new framework (as the other Reviewers point out, many components of our approach have been touched on by previous work). The novelty and impact of our work lies in connecting a Bayesian statistical approach to the problem of limited and uneven sampling (driven by difference in species abundances, detectabilities, constrained time and budgets, etc.) and, we hope, in making this method more accessable to those without extensive statistical or modelling experience. Because of the difference between Reviewer 2 and the other Reviewers, we have opted to prioritise the majority view and focused first on comments by Reviewers 1, 3, and 4. We hope that, in the course of these revisions, we have at least partially adressed Reviewer 2's concertns as well.

@@

\newpage

% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Reviewer \#1}
% ---------------------------------------

	1. Suggestion to refocus on prior selection

	\begin{refquote}
	Below I offer my thoughts on this well-written manuscript. Normally I condense my review into a few key points, but I found myself uncharacteristically divided with the paper as presented. At first, the introduction covers ground very well-trod by prior works and doesn’t really address its contribution. I was mostly frustrated by the rehashing of topics made by many previous papers, include many by the authors themselves. But then the paper seems to morph and pick up steam on L248. Rather than reaching towards an amorphous and grandiose “quantitative framework”, the authors briefly zoom into a very concise, and hugely important, question of choosing prior distributions for harnessing information among networks. This has been completely unexplored and merits attention. In ecology more broadly, priors are treated with timidity, as if we couldn’t dare to leverage past work on our current understanding. Personally, I have always felt limited by this standard. I applaud the authors for taking on this challenge, and I would like to see an introduction that merits and debates this question in much more detail. When should we use prior information? How do we go about constructing informed priors for networks? When can we use priors from the data in question? This is sometimes called approximate bayes (http://andrewgelman.com/2016/03/25/28321/), or empirical bayes, perhaps alluded to in the title, but not fully explained in the introduction. Should empirical priors be drawn from hyperpriors or fixed for each interaction? Can we combine qualitative information and quantitative information? This is all exciting ground that will open up new avenues for networks. Walking the reader through flat priors, informed priors and empirical priors is crucial for the importance of analysis to be understood by the reader. The use of empirical priors can be quite controversial, and should be atleast touched on in the discussion. \\
	I’ve left my comments below on the introduction, but in my opinion, it should be almost wholly rewritten in favor of a more targeted question constructing networks using priors, which is the key novelty of the work and is mostly hidden by the current introduction. I’m not convinced any new analysis needs to be done, which speaks to the conflict between the current introduction and the actual data presented. I see the makings of a really nice paper here, and I’m confident the authors will be able to achieve this text revision.
	\end{refquote}

	\textbf{R:} [[Definitely should expand this, but do we want to really focus on those?]][[not quite done]]

	2. Suggestion to add more literature

	\begin{refquote}
	The introduction flows well and is thoughtfully laid out. Given the enormous amount of literature in the field, it is not possible to provide a full set of citations. However, it seems remiss to not consider Jordano (2016) in the sampling section.
	\end{refquote}

	\textbf{R:} We thank the Reviewer for their compliments to our introduction and for the recommendation of Jordano 2016. We have incorporated this reference as suggested. Following comments from other reviewers, we have refined and slightly restructured our introduction in the hope of more clearly establishing the goal of our manuscript ('narrowing our net'. We hope that this revised introduction will also meet with the Reviewer's approval. [[done]]

	3. Suggestion to de-emphasize MLE estimate and get straight to Bayes

	\begin{refquote}
	It’s a bit confusing to lead the reader towards a Bayesian analysis, and then immediately start with the MLE estimate. Why is this needed at all? (L162-186). Just start at 187?
	\end{refquote}

	\textbf{R:} The section on the MLE estimate was designed to illustrate the large sample sizes needed in the absence of a Bayesian framework. Upon reflection, we see have moved this demonstration to a box dealing specifically with sampling. We now begin with the Bayesian beta distribution as suggested. [[I think done?]]

	4. Suggestion to remove moments of the beta distribution

	\begin{refquote}
	I think a bit of space is wasted on defining the moments of the beta distribution. This is very googleable, and almost too thorough. I think the space is better utilized aligning the ecological challenge and the quantitative method.
	\end{refquote}

	\textbf{R:} While we feel that a short introduction to the beta distribution is important to bring researchers new to Bayesian statistics up to speed (and give them some keywords to Google), we accept the Reviewer's suggestion to reduce the amount of space given to the beta. We have therefore moved the description of basic properties to Appendix S2. The remaining paragraph introducing the beta distribution now leads directly into the section describing prior selection.

	5. Novelty of the study not clear in current framing

	\begin{refquote}
	I’m wrestling with the novelty of the work as presented and whether it reaches the standard for publication at MEE. Certainly, much of this logic is laid out in other works. The authors are well aware of this and have made significant contributions to this topic in the last few years. In particular, the authors should try to be much more explicit about the contribution they hope to offer that hasn’t been covered. I could list atleast two dozen papers here, but some key ones might include ...	All have the theme of detection, occurrence and interaction as a central challenge in constructing reliable networks. Several prior papers have offered Bayesian approaches, starting with the individual model by ...
	While it is true that none of the above papers do the exact same thing as this manuscript, they all	orbit the same topic. 
	\end{refquote}

	\textbf{R:} We thank the Reviewer for the literature suggestions and now include them in our introduction and/or discussion. We emphasize the board applicability of our appraoch across network types and where species traits affecting interaction probability may not be known. [[Make sure this comes through]] We hope that the contribution our manuscript makes is now clearer.

	6. Potential contradiction

	\begin{refquote}
	L89 for example, seems to conflict with the two paragraphs immediately following it?
	\end{refquote}

	\textbf{R:} [[]]

	7. Final comment on framing the study

	\begin{refquote}
	At the same time, the paper is clear and very readable. I wholly support the method and I think it is something critical that needs to be adopted by the community. \\
	Having read the paper several times, I think that the authors are trying to cast their net too widely, even starting from the title. From that perspective, they don’t meet the expectation of new insight. However!! I was extremely interested in the brief discussion on using prior knowledge, especially the delicacy of trying to transfer information among networks (L248). My recommendation is to drastically reduce the grandiose attempt at a “quantitative framework for networks” (L1 – L246) and really zoom in on the contribution of transferring information among networks through informed priors.	Again L278, this is very well covered in concept by recent papers in MEE that include the authors of this work, as well as several by Weinstein, Bartomeus and others.
	\end{refquote}

	\textbf{R:} We thank the Reviewer for their compliments and accept their suggestion that we are somewhat overexcited about our approach. We have refined the introduction to be more specific about the problem we are attempting to solve. We have also expanded our treatment of prior selection and hope that our paper now reads as achieving its goal.

	% 	Literature suggestions:
	% Jordano, P. (2016). Sampling networks of ecological interactions. Functional Ecology, 30(12), 1883–1893. doi:10.1111/1365-2435.12763
	% Bartomeus, I. (2013). Understanding Linkage Rules in Plant-Pollinator Networks by Using Hierarchical Models That Incorporate Pollinator Detectability and Plant Traits. PLoS ONE, 8(7), 1–9. doi:10.1371/journal.pone.0069200
	% Poisot, T., Cirtwill, A. R., Cazelles, K., Gravel, D., Fortin, M.-J., & Stouffer, D. B. (2016). The structure of probabilistic networks. Methods in Ecology and Evolution, 7(3), 303–312. doi:10.1111/2041-210X.12468
	% Poisot, T., Stouffer, D. B., & Gravel, D. (2015). Beyond species: why ecological interaction networks vary through space and time. Oikos, 124(3), 243–251. doi:10.1111/oik.01719
	% Graham, C. H., & Weinstein, B. G. (2018). Towards a predictive model of species interaction beta diversity. Ecology Letters. doi:10.1111/ele.13084
	% Gravel, D., Poisot, T., Albouy, C., Velez, L., & Mouillot, D. (2013). Inferring food web structure from predator-prey body size relationships. Methods in Ecology and Evolution, 4(11), 1083–1090. doi:10.1111/2041-210X.12103
	% Wells, K., & O’Hara, R. B. (2013). Species interactions: Estimating per-individual interaction strength and covariates before simplifying data into per-species ecological networks. Methods in Ecology and Evolution, 4(1), 1–8. doi:10.1111/j.2041-210x.2012.00249.x

@@

	\end{refquote}

	Minor points:

	-l.62: define formally T
	-l.244: this is weird to mention that the analysis has been done on another dataset but that the results will not be discussed… What is the interest for the reader?
	-l.149: since the authors consider the interactions are independent, there is morally no network in the approach (except the result)
	-l.252: not clear. Why this choice?
	-l.259: not clear
	-l.278: the authors investigate the consequence of uncertainity on network metrics. This question is of peculiar interest, but here it is restricted to the connectance and nestedness. Why these two metrics? Why not others? What is the impact of integrating incertainity into the metrics computation? (we guess the answers but we could expect the authors develop these points).
	l.291: explain better the simulation procedure
	l.306: given the shape of the distribution (exponential), the mean is not an appropriate indicator.
	l.327: what does it mean? How is it possible?

% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Referee \#3}
% ---------------------------------------

	\begin{refquote}
	Comments to the Corresponding Author
	Overall, I think this is a very good paper and makes an important contribution.  I think there are three main ways it can be improved:
	\end{refquote}

	\textbf{R:} [[Move the end bit up here?]]

	1. Add more references to the literature

	\begin{refquote}
	1.      The simplest – do a better job of acknowledging what else has been done in the field – much of which has actually been done by the authors and their collaborators.  Given that they know there work I won’t point that out (but they are under-siting this literature a bit) but they could consider Graham and Weinstein on-line early 2018 (I realize that this was just out when the author’s submitted but it has some very similar messages) and the empirical example of Weinstein and Graham in Ecology letters 2017.  I don’t think this would in any way diminish the importance of the current paper because I think the challenge in network ecology is to get people to use better quantitative methods.
	\end{refquote}

	\textbf{R:} We had not intended to write a review paper and did not wish to over-cite ourselves, but we take the Reviewer's point and have expanded our references to the literature. We have taken particular care to add references to Graham/Weinsten papers as two of the reviewers suggested work by these authors. We hope that we now adequately acknowledge previous work.

	2. Confusing terminology

	\begin{refquote}
	2.      Provide more clarity in descriptions making sure to consider how terms and ideas have been used previously.  Two things come to mind – the use of terms and distinction between interaction and process uncertainty; and the somewhat contradictory sounding statements about if sampling more is actually good.
	\end{refquote}

	\textbf{R:} [[interaction and process uncertainty...]] We respond to the Reviewer's comments about sampling below.

	3. Introduction of the case study seems off-topic and illogical.

	\begin{refquote}
	3.      The set up (introduction) to the case study is quite odd and somehow seems off topic – or at least not logical based on what the reader has read up to that point.
	\end{refquote}

	\textbf{R:}

@@

	4. Misunderstanding of our point about sampling effort

		\textbf{R:} We believe that the Reviewer has badly misunderstood the point of our comments on sampling effort. Several of their comments suggest that we are advocating for reducing sampling effort. This is emphatically not the case. Rather, we assumed that field researchers already sample to the maximum extent possible given their time and resource constraints and so a call to "sample more" would not be helpful. We now address this assumption explicitly in a box dedicated to the potential for sampling effort to reduce uncertainty about interactions. Below, we address the Reviewer's sampling-related comments one by one.

		\begin{refquote}
		Line 94.  I find this a very odd argument against sampling multiple times.  So, if you sample more you might see more then understand the system less?  The logic does not make sense to me. 
		\end{refquote}

@@

		\textbf{R:} I do not know how the Reviewer assumes that we are against repeat sampling when this is, in fact, one of the core parts of our approach. Our point here is that some species (e.g., cryptic or difficult-to-identify species) and interactions (e.g., brief visits of pollinators to plants) are difficult to detect and may be missed even with multiple sampling. If a rare species is only detected in one sampling round, then the repeated sampling necessarily tells us little about its interactions. For species which are frequently detected, we absolutely learn about the detection probability of their interactions with repeated sampling.

		\begin{refquote}
		Line 130.  The ideas here are largely a repeat from those above.  Further, while it may be true that we can sample too much – I think it is dangerous to suggest we should sample less – do the authors think that sampling across most network studies is sufficient (the opposite is stated in the discussion)?  I wonder if the argument is a bit more statistical than biological.
		\end{refquote}

		\textbf{R:} We agree that it is dangerous to suggest that anyone sample less, that is why we have not done so. We argue only that the amount of sampling required to be confident that co-occurring species do not interact is large -- likely beyond what is feasible for speciose systems given the limited resources available to many researchers. Sampling across most network studies is almost certainly not sufficient, but data which would allow readers to judge this (i.e., number of times each species is observed, independent of numbers of observed interactions) is not generally provided. We chose to be more charitable than the Reviewer and assume that those compiling empirical networks are sampling as much as possible given the constraints of their system and available resources. Infite sampling would, of course, be the best option but it is unlikely that researchers will be able to perpetually increase sampling.

		\begin{refquote}
		Line 144.  I am much more comfortable with this statement than how sampling effort should be considered and I would suggest moving this up and then explaining how even if we sample well we need to consider uncertainty for the reasons you mention in the previous section.  Please note that you make the same point in your discussion on line 338.
		\end{refquote}

		\begin{refquote}
		Line 319.  It is clear that these are large samples but if interaction among co-occurring species was greater than you need lower samples – correct?  Should this be made clear?  Otherwise, we maybe can just never get enough data!
		\end{refquote}

		\begin{refquote}
		Line 338 to 342.  Throughout I am confused if the authors suggest more sampling is good or bad…  At the end of the paragraph it seems it isn’t so great to sample more because you end up with these annoying “0” values…??????
		\end{refquote}

@@

	Below I provide specific comments

		5. Rephrase to acknowledge prior work

		\begin{refquote}
		Line 7.  It is certainly true that most networks are snapshots in time but there is a growing realization – including some nice examples (including those by the authors) that address this issue.  Maybe what you want to say is that we know that networks should not be considered static but we lack the tools – or ability to collect data – or whatever you think is the cause – to correct this situation. 
		\end{refquote}

@@

		6. Redundancy

		Line 23.  Delete the “because” (you have one in the sentence already).

		\textbf{R:} Done.

		7. Increase references to prior work

		\begin{quotation}
		Line 30.  There are several conceptual and empirical attempts to consider detection probability – why aren’t these cited (work by Bartomeus comes to mind).\\

		Line 36.  I certainly see value in the approach and the general ideas of these authors in particular but they should acknowledge the work that has been done by themselves and others!\\

		Line 89.  In Weinstein and Graham (Ecology Letters) the processes modeled were trait matching (which you place in interaction uncertainty) and abundance (which is perhaps your process uncertainty??).  I find myself quite confused based on how you describe things in this MS (See text above) and how you cite the literature.\\

		Line 148.  Please note that a paper with a very similar aim was recently published (Graham and Weinstein).  This does not to diminish the value of this study in any way, as multiple perspectives on quantitative solutions in network ecology are urgently needed….. but the other work should be considered. More generally, the introduction does not really do justice to what has been done already – even the authors own work.  The problem in my view is that the community using better statistics – of which the authors are very important members – has not managed to communicate to most people studying networks and better methods are simply not being adopted.  The current paper is a very nice attempt to show the broader community that the Bayesian approach is not so complex and has many advantages.  I think this is a very important message and is what makes this paper an important contribution.  Further, the approach to parse out different types of uncertainty and suggestions for how to come-up with informative priors – is very useful.  The theory/method is well developed overall and provides an example – which is great.\\
		Line 288.  I am pretty sure this idea is in the literature several times and should be cited.  Isn’t this the same as drawing a probability of interaction from a distribution where the distribution of each interaction is an output of the Bayesian method?\\
		Line 352 – 358.  Citations are needed in this section as this has been suggested before.
		\end{refquote}

		\textbf{R:}

		8. Potential for confusion about "process" nomenclature

		\begin{refquote}
		Line 86.  So, similar factors (i.e., trait matching) can be used to detect different kinds of uncertainty.  Should this be stated?  You might also consider a different word that process as “observation models” and “process models” are commonly used terms in Bayesian stats and in this case “process” often considers what you call “interaction”.  There are some interesting to attempts to model co-evolution that consider similar ideas (i.e., a barrier to interaction and then trait-matching; but maybe outside of the scope of this MS). While I appreciate that your naming has merit, I think if your hope is that more ecologists use these methods then the terminology should be consistent across papers/approaches to the greatest extent possible.
		\end{refquote}

		\textbf{R:} Interesting... [[not done, do we want to?]]

		9. Reduce repetition of inevitable uncertainty

		\begin{refquote}
		Line 73, 87.  Maybe the idea that some uncertainty is “inevitable” should not be repeated in multiple sections.  Either find a different way of saying it – or state it in your introductory paragraph and then don’t keep repeating.
		\end{refquote}

@@

			\begin{quotation}

				Until these gaps are filled, some interaction uncertainty will remain.

			\end{quotation}

		10. Why not always model probabilities of co-occurrance?

### 2018-11-22 manuscript/CI_interactions.tex
more revisions

\section*{Abstract}

  \begin{enumerate}

@@

    Representing an ecological community as a network allows ecologists to address both community composition and the interactions between species~\citep{Roslin2016}. Identifying these interactions is a crucial step towards understanding (and predicting) the effects that species have on each other and the response of the community as a whole to external perturbations~\citep{Bartomeus2016,Giron2018}. Importantly, information is conveyed both by the presence and \emph{absence} of links between species. Presences and absences are not, however, equally certain. An observed link definitely occurred, but there are multiple reasons why a given link may not be observed.

    First and foremost, ecological communities are known to be stochastic~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilites and hence in interactions~\citep{Vazquez2005,Poisot2015,Graham2018}. Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013}. Even assuming constant co-occurrence within a given study system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012,Emer2018}, time~\citep{Kitching1987,Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}, throughout life cycles~\citep{Preston2014,Clegg2018}, and with environmental conditions~\citep{Poisot2015}.

    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeeus2013,Poisot2016}. Efforts in this vein usually take the form of creating model food webs that approximate observed empirical networks~\citep{Allesina2008,Williams2010,Rohr2016}. These models may be based on species traits and/or abundances~\citep{Rohr2016,Graham2018,more} or on simple abstract rules~\citep{Allesina2008,Williams2010}. Such networks provide an important ''reality check'' by allowing us to compare the observed network to what would be expected under a particular set of assumptions~\citep{Bartomeus2013,Weinstein??}. They allow us to estimate the numbers of interactions which have not been observed and predict which unobserved interactions are most likely~\citep{Bartomeus2013}.

@@

    We can create a simple Bayesian approach to modelling the probability of an interaction occurring ($\lambda$) by combining a maximum likelihood estimate of $\lambda$ with a prior distribution (described in the next section) and a normalising function. The MLE of $\lambda$, based on the number of observed interactions $k$ and observed co-occurrances $n$ is $\lambda = \frac{k}{n}$. The most appropriate prior distribution for a probability such as $\lambda$ is the beta distribution:

@@

    \subsubsection*{Choosing a prior distribution}

@@

      The choice of prior will depend on the information available. In general, it is best to use a prior taken from a similar system as emphasised above. If such data are not available, a prior based on many networks with a similar level of resolution could be useful, as could a prior based on a preliminary round of sampling (analogous to ``training data"). If there is no suitable informative prior, it is best to use an explicitly uninformative prior. While an uninformative prior will not greatly reduce variance about $\lambda$, it does clearly state our lack of prior knowledge and will not bias our conclusions.

  \subsection*{An empirical example}

      To illustrate the process of constructing a Bayesian network, we use the comprehensively-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}. This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations. The data were collected over 29 years at 374 unique locations across Europe. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S4} for details).

@@

  Based on the framework described above, we can now offer some recommendations for improved descriptions of ecological interactions. First, sample sizes should be as large as possible in order to reduce detection uncertainty. Second, where sampling on the order of 30-50 observations per species pair is not possible (i.e., in most cases), researchers should acknowledge the varying levels of confidence surrounding interactions between different species pairs. Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable. Third, the uncertainty around interactions should be incorporated in calculations of network properties. Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates. This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to estimates of network properties. This will allow us to say whether networks have different structures \emph{and} whether those differences are greater than we would expect given the inherent variability of interactions. To facilitate the practical application of these recommendations, we provide all code used in this paper in the supplementary material.

>>>>

\section*{Abstract}
  [[was fine? Maybe lightly edit to make clear we're not doing a review]]
  \begin{enumerate}

@@

    Representing an ecological community as a network allows ecologists to address both community composition and the interactions between species~\citep{Roslin2016}. Identifying these interactions is a crucial step towards understanding (and predicting) the effects that species have on each other and the response of the community as a whole to external perturbations~\citep{Bartomeus2016,Giron2018}. Importantly, information is conveyed both by the presence and \emph{absence} of links between species. Presences and absences are not, however, equally certain. An observed link definitely occurred, but there are multiple reasons why a given link may not be observed~\citep{Jordano2016}.

    First and foremost, ecological communities are known to be stochastic~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilites and hence in interactions~\citep{Vazquez2005,Poisot2015,Graham2018}. Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013}. Even assuming constant co-occurrence within a given study system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012,Emer2018}, time~\citep{Kitching1987,Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}, throughout life cycles~\citep{Preston2014,Clegg2018}, and with environmental conditions~\citep{Poisot2015}.

    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007,Jordano2016}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeeus2013,Poisot2016}. Efforts in this vein usually take the form of creating model food webs that approximate observed empirical networks~\citep{Allesina2008,Williams2010,Rohr2016}. These models may be based on species traits and/or abundances~\citep{Rohr2016,Graham2018,more} or on simple abstract rules~\citep{Allesina2008,Williams2010}. Such networks provide an important ''reality check'' by allowing us to compare the observed network to what would be expected under a particular set of assumptions~\citep{Bartomeus2013,Weinstein??}. They allow us to estimate the numbers of interactions which have not been observed and predict which unobserved interactions are most likely~\citep{Bartomeus2013}. Alternatively, it is possible to estimate the number of unobserved interactions which likely occurred~\citep{Jordano2016}. This...

@@

    We can create a simple Bayesian approach to modelling the probability of observing an interaction ($\lambda$) by combining a maximum likelihood estimate (MLE) of $\lambda$ with a prior distribution (described in the next section) and a normalising function. The MLE of $\lambda$ can be modelled as a Bernoulli trial based on the number of observed interactions $k$ and observed co-occurrances $n$: $\lambda = \frac{k}{n}$. The most appropriate prior distribution for a probability such as $\lambda$ is the beta distribution:

@@

    \subsubsection*{Choosing a prior distribution}  [[expand]]
      [[expand]]

@@

      The choice of prior will depend on the information available and the question of interest. In general, it is best to use a prior taken from a similar system as emphasised above. If such data are not available, a prior based on many networks with a similar level of resolution could be useful, as could a prior based on a preliminary round of sampling (analogous to ``training data"). If there is no suitable informative prior, it is best to use an explicitly uninformative prior. While an uninformative prior will not greatly reduce variance about $\lambda$, it does clearly state our lack of prior knowledge and will not bias our conclusions. Similarly, if detailed information is available but refers to the question at hand, it is best to use a less informative prior so as not to force a particular result. For example, if researchers are interested in testing whether body-size ratios affect probabilities of interaction they should not use a prior which predicts interactions based on body sizes.

      \textbf{Uninformative priors}

        An uninformative prior is chosen so as not to bias the posterior distribution in any particular direction. That is, all of the information will come from the observed data. For pairs of species with little or no observed data, an uninformative prior will leave large variance about $\lambda$ and reflect our lack of knowledge about the pair. Since we model $\lambda$ as a Bernoulli trial, the appropriate uninformative prior is Jeffreys prios: a beta distribution with $\alpha$=$\beta$=0.5. The sum of $\alpha$ and $\beta$ is roughly equivalent to the weight of the prior, so Jeffreys prior has equal weight to a single observation. An uninformative prior is most appropriate when considering a novel system or a system where the only prior knowledge available directly relates to the question we wish to analyse.

      \textbf{Informed priors}

        In most cases, researchers will be able to draw upon prior knowledge for at least some interactions. One very simple example is the assumption that, in a food web, plants will not consume any prey. There is very little uncertainty around the lack of a observed predation of any plant upon any animal in the system, regardless of how often the plant and animal are observed together.

        [[addressing different types of uncertainty]]
        [[drawing upon system-specific or broader knowledge]]

        If we are interested only in interactions which occur in the focal system under current environmental conditions, we might use a prior which includes probabilities of co-occurrence. That is, we could limit the set of potential interactions to pairs of species which currently co-occur~\citep{Gravel2013}, condition probabilities of interaction on probabilities of co-occurrence based on abundance~\citep{}, etc. Note that such models lump together interaction uncertainty and process uncertainty and are only concerned with measuring detection uncertainty. Whether or not this is appropriate will depend upon the question of interest.

        If traits governing interactions are known (e.g., body size in food webs~\citep{Gravel2013} or corolla depth in pollination networks~\citep{Graham,Weinstein}), then trait-based models may be used as a prior. Such models address interaction uncertainty directly (i.e., they estimate whether a pair of species \emph{can} interact, regardless of whether they are likely to encounter each other). To address both interaction and process uncertainty, a researcher might combine trait-based and co-occurrence models into a single prior. Such a model would reduce the uncertainty about unobserved interactions, but at the cost of adding more assumptions about the study system. This type of very detailed prior is therefore most appropriate in very well-understood systems where a great deal of expert knowledge can be applied.

      \textbf{Empirical priors} [[using data from the data in question]][[contentious]][[should these be drawn from hyperpriors or fixed for each interaction]]

  \subsection*{An empirical example}
    [[Make the point of this clearer]]
      To illustrate the process of constructing a Bayesian network, we use the comprehensively-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}. This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S4} for details).

@@

  Based on the framework described above, we can now offer some recommendations for improved descriptions of ecological interactions. First, sample sizes should be as large as possible in order to reduce detection uncertainty. Second, researchers should acknowledge the varying levels of confidence surrounding interactions between species pairs. In the absence of strong prior information a very high level of sampling (i.e., 30-50 observations in our example) is needed \emph{for each species pair}. This is not likely to be possible for most studies. including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable. Where there are strong prior expectations about pairs of species that will not interact, these should be explicitly stated so that readers know which zeros in an interaction matrix are based on observed data and which are based primarily upon expert knowledge. Third, the uncertainty around interactions should be incorporated in calculations of network properties. Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates. This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to estimates of network properties. This will allow us to say whether networks have different structures \emph{and} whether those differences are greater than we would expect given the inherent variability of interactions. To facilitate the practical application of these recommendations, we provide all code used in this paper in the supplementary material.
